### 2019-07-23 initial/notes.tex
stash

>>>>

Now, this turns out to be slightly inaccurate for $f > 0$, probably because
$\mathcal{C}_{\pm}$ is a function of $\eta$ and changes over the course of
orbit. The two possible solutions are: compute $\eta_\star$ averaged over the
trajectory (for numerical purposes) or to compute the analytical correction for
a given $\eta$. The latter seems hard, so we'll go with the former.
